\sysfull

### 2018-04-13 paper/evaluation.tex

We compare \sys against state-of-the-art task-based runtime Chain~\cite{chain}.
We do not compare \sys to other, earlier systems, such as DINO~\cite{dino} or
Mementos~\cite{mementos} (cf. Section~\ref{sec:background_consistency}), as
Chain is the only task-based execution model available to which we can compare
\sys.

We evaluated \sys using benchmarks from the literature~\cite{chain,alpaca} and
several new programs: (i) \textbf{bc}: counts bits in byte pseudo-random string
using several algorithms, and compares results for correctness; (ii)
\textbf{cem}, which emulates an embedded temperature sensing engine and in
which measurements are randomly generated and compressed using LZW with a fixed
entry dictionary and fixed byte block; (iii) \textbf{cuckoo}: which implements
a Bloom-filter-like Cuckoo filter that first hashes a sequence of pseudo-random
numbers, then queries the filter to recover the sequence; (iv) \textbf{rsa}:
which encrypts a fixed string with a stored key; (v) \textbf{ar}: which
performs nearest neighbour classification of randomly generated data modelling a
three-axis accelerometer. This set of benchmarks overlaps with those used
in~\cite{chain,alpaca}. We implemented several new applications: (vi)
\textbf{sort}: selection sort algorithm on a fixed sequence of numbers, and
(vii) \textbf{dft}: discrete Fourier transform. All applications are compared
in columns eight and nine of Table~\ref{table:compiler_result} showing the
number of source lines of code compared to Chain.

%\begin{table}[t]
%	\centering
%	\footnotesize
%	\begin{tabular}{|c|c|c|}
%		\hline
%		Application & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
%		\hline\hline
%		{bc} & 351 & 588 \\ %59\%
%		{cem} & 388 & 721 \\ %53\%
%		{cuckoo} & 483 & 762 \\ %63\%
%		{rsa} & 887 & 1233 \\ %71\%
%		{ar} & 483 & 762 \\ %63\%
%		{dft} & {} & {} \\ %Two resolutions: 4 and 8 Bytes
%		{dd} & {} & {} \\ %Data decompression size: 100 bytes
%		{sort} & {} & {} \\
%		\hline
%	\end{tabular}
%\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
%\label{table:benchmark_list}
%\end{table}

@@

\begin{table}[t]
	\centering
	\footnotesize
	\renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{|l|cc|cc|cc|cc|c|}
		\hline
		{} & \multicolumn{2}{c|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & 180 & 287 & $<$1\\
		dft$^\dagger$ & --- & --- & --- & --- & --- & --- & 222 & 293 & ---\\
		%dd &  &  &  &  &  &  &  & 287 &  \\
		\hline
	\end{tabular}
	\caption{\textbf{Comparison between \sys and Chain source code line number (SLOC column) and comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Man.) (other columns)}; $^\dagger$dft does not compile with Clang}\label{table:compiler_result}\vspace{-0.5cm}
\end{table}

\textbf{\sys Compiler Generated Code Characterization.} The behaviour and the efficiency metrics of the \sys compiler are given in Table~\ref{table:compiler_result}. 
%
%for each application, for manually written (Man.) and automatically compiled (Comp.) benchmarks the difference in the number of bytes of protected data (columns 2 and 3), the number of tasks (columns 4 and 5), the number of \sys protected data API access calls (columns 6 and 7), the lines of code in each application for \sys and Chain (columns 8 and 9), and compilation time using \sys's compiler (column 10).
%
On average, compiler-generated code introduces about 0.3\% more bytes of protected data, suggesting that liveness analysis captures natural boundaries in the use of variables also caught by a manual implementation. Compiler-generated code generates about 16\% fewer tasks for applications, on average. The results indicate that the \sys compiler selects task boundaries differently than a programmer would manually, favoring fewer, larger tasks. The \sys compiler inserts protected data access operations conservatively when a variable {\em may} alias a protected variables, due to the limitations of pointer aliasing. Consequently, the \sys compiler introduces 48\% more protected data accesses than programmer-written code. The run time results in Section~\ref{sec:result_compiler_time} show that the increase in protected data
accesses sometimes degrades performance. Overall, the data show that the compiler automatically generates tasks similarly to manually written tasks. Doing so, \sys's compiler reaps the static task benefits of \sys, but simplifies programming by sparing the programmer the job of task decomposition.

>>>>

%We compare \sys against state-of-the-art task-based runtime Alpaca~\cite{alpaca}. We do not compare \sys against Chain~\cite{chain}, another task-based system, which is inferior to Alpaca in its performance. Also, we do not compare \sys to checkpointing-based systems, such as DINO~\cite{dino} or Mementos~\cite{mementos} (cf. Section~\ref{sec:background_consistency}), as both of them are build on top LLVM compiler, which performance is inferior to GCC compiler used in the evaluation of \sys \todo{Please check if the LLVM compiler argument makes sense}.

%We evaluated \sys using benchmarks that originated from the MiBench testing suite~\cite{mibench,hicks_mibench2_2016}. Specifically, we have implemented three benchmarks used by Chain~\cite{chain} and Alpaca~\cite{alpaca} (source code: \cite{coala_website}), namely: \textbf{ar}: nearest neighbor classification of randomly generated data modeling a three-axis accelerometer; \textbf{bc}: counts bits in byte pseudo-random string using several algorithms, and compares results for correctness; \textbf{cuckoo}: Bloom-filter-like Cuckoo filter that first hashes a sequence of pseudo-random numbers, then queries the filter to recover the sequence. Additionally, we have ported three new benchmarks from~\cite{mibench}, namely: \textbf{fft}: Fast Fourier Transform algorithm \todo{specify details of the implementation}; and \textbf{sort}: selection sort algorithm on a fixed sequence of numbers. \todo{justify the selection of these benchmarks} All applications are summarized in Table~\ref{table:compiler_result} in terms of memory footprint, source lines of code and number of tasks. \todo{update table with new data}

@@

\begin{table}[t]
	\centering
	\footnotesize
	\renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{|l|cc|cc|cc|cc|c|}
		\hline
		{} & \multicolumn{2}{c|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & 180 & 287 & $<$1\\
		dft$^\dagger$ & --- & --- & --- & --- & --- & --- & 222 & 293 & ---\\
		%dd &  &  &  &  &  &  &  & 287 &  \\
		\hline
	\end{tabular}
	\caption{\textbf{Comparison between \sys and Chain source code line number (SLOC column) and comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Man.) (other columns)}; $^\dagger$dft does not compile with Clang }\label{table:compiler_result}\vspace{-0.5cm}
\end{table}

%

\textbf{\sys Compiler Generated Code Characterization.} The behaviour and the efficiency metrics of the \sys compiler are given in Table~\ref{table:compiler_result}.  \todo{update table with new data}
%
%for each application, for manually written (Man.) and automatically compiled (Comp.) benchmarks the difference in the number of bytes of protected data (columns 2 and 3), the number of tasks (columns 4 and 5), the number of \sys protected data API access calls (columns 6 and 7), the lines of code in each application for \sys and Chain (columns 8 and 9), and compilation time using \sys's compiler (column 10).
%
On average, compiler-generated code introduces about 0.3\% more bytes of protected data, suggesting that liveness analysis captures natural boundaries in the use of variables also caught by a manual implementation. Compiler-generated code generates about 16\% fewer tasks for applications, on average. The results indicate that the \sys compiler selects task boundaries differently than a programmer would manually, favoring fewer, larger tasks. The \sys compiler inserts protected data access operations conservatively when a variable {\em may} alias a protected variables, due to the limitations of pointer aliasing. Consequently, the \sys compiler introduces 48\% more protected data accesses than programmer-written code. The run time results in Section~\ref{sec:result_compiler_time} show that the increase in protected data
accesses sometimes degrades performance. Overall, the data show that the compiler automatically generates tasks similarly to manually written tasks. Doing so, \sys's compiler reaps the static task benefits of \sys, but simplifies programming by sparing the programmer the job of task decomposition.
